Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing

### 2021-10-21 00-ES/PubliER/Draft.tex
First real PPQS 21-10-2021-PPQS.pdf

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  14pt,
]{extarticle}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Distributed recycling for additive manufacturing: an ecosystem services perspective},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=2cm, right=2cm,top=3cm,bottom=2cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{float}
\usepackage{subfig}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{pdflscape}
\usepackage{svg}
\usepackage{lineno}
\usepackage{setspace}
\newcommand*{\doverline}[1]{\overline{\overline{#1}}}
\usepackage{tabu}

@@

\title{Distributed recycling for additive manufacturing: an ecosystem services perspective}
\author{}
\date{\vspace{-2.5em}}

@@

The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg 2020}).
No country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
Therefore, it is no possible to rely only on techno-centric interventations without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
We need to integrate ecological carrying capacity since the fuzzy front end phase of a industrial systems.

However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.
The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements.
As a case application, the study of distributed recycling manufacturing will be describe.
Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al. 2021}).
Therefore, new approaches need to be explored in order to reduce ar at least recycling this material.
Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.

@@

\textcolor{red}{to complete ... }

@@

\hypertarget{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}{%
\subsection{Ecosystems services in the industrial systems: towards a reconciliation of two capitals for humanity.}\label{ecosystems-services-in-the-industrial-systems-towards-a-reconciliation-of-two-capitals-for-humanity.}}

The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the human activites' impacts on the earth remained marginal. This scenario is not true today.
The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al. 2019}).
It is difficult to provide information about pressure from industrial systems in corporate information systems.
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-ref}{\textbf{ref?}}).

According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al. 2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
Among the root causes of ecological degradation is ignorance about the exceedance of the ecological carrying capacity in many desicions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}).
Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).

\protect\hyperlink{ref-Ceschin2016}{Ceschin and Gaziulusoy} (\protect\hyperlink{ref-Ceschin2016}{2016}) putted forward the evolution of \emph{Design for Sustainability (DfS)} framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.
\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
THe main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.

@@

Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) priorization of the territorial issues, and 3) identification of the industrial issues.

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{|p{1.00in}|p{1.50in}|p{1.50in}|p{2.00in}}

\caption{Terminology used in the deifnition of the spheres}\label{tab:Terminology}\\

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\

\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}->{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=2pt}-}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Terminology}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Definition}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Exemple}}} \\

\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}\endhead

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Techno-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Equipement\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Detailed\ models}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Corn\ production\ at\ a\ location}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Value\ chain\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ activities}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Average\ corn\ production\ in\ a\ region}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Economy\ scale}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Industrial\ sectors}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Grain\ farming\ sector}}} \\

\noalign{\global\setlength{\arrayrulewidth}{1pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Eco-sphere}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecosystem\ Services\ (ES)}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Benefits\ humans\ received\ from\ Nature}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Serviceshead}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Area\ providing\ the\ ES\ to\ specific\ users\ of\ that\ servicee}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ demand}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Emissions\ and\ resource\ use\ by\ technological\ systems}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{ES\ supply}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 1.5in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{Ecological\ capacity\ to\ mediate/sequester/absord\ impacts}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\raggedright}p{\dimexpr 2in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{}}} \\

\noalign{\global\setlength{\arrayrulewidth}{2pt}}\arrayrulecolor[HTML]{000000}\cline{1-4}

\end{longtable}

\begin{figure}[!ht]
\includegraphics[width=1\linewidth]{Figures/Systemes} \caption{Notation for assessing techno-ecological synergies}\label{fig:Fig-spheres}
\end{figure}

\hypertarget{territorial-issues}{%
\subsubsection{Territorial issues}\label{territorial-issues}}

More than two thirds of the world's population are expected to live in cities by 2050 (\protect\hyperlink{ref-ref}{\textbf{ref?}}). Thus, the integration of ecosystem services in the urban and peri-urban planning is a key issue for on quality of life in cities (\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton 2013}).
Urban ecosystems are especially important in providing services with direct impact on health and security such as air purification, noise reduction, urban
cooling, and runoff mitigation (\protect\hyperlink{ref-Bolund1999}{Bolund and Hunhammar 1999}).
\protect\hyperlink{ref-Gomez-Baggethun2013}{Gómez-Baggethun and Barton} (\protect\hyperlink{ref-Gomez-Baggethun2013}{2013}) draws on the developments of the ecosystem services for urban planning.
They formulated a classification of ecosystem services and disservices in urban areas, including valuation methods and tools.

The main purpose in this step is the identification of the main urban priorities in the territorial context, from a perspective of ecosystem services.

example, if agroecosystems are critical for food production, wetlands for nutrient cycling, and forests for carbon sequestration,
Which ecosystem services in a given city are most relevant varies greatly depending on the environmental and socio-economic characteristics of each site.

\textcolor{red}{ To complete based on articles that reading on Sabrina (so far) ...}

\hypertarget{industrial-issues}{%
\subsubsection{Industrial Issues}\label{industrial-issues}}

\textcolor{red}{ To complete based on article that reading on...}

\hypertarget{definition-of-the-tech-sphere}{%
\subsubsection{Definition of the Tech-Sphere}\label{definition-of-the-tech-sphere}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{float}
\usepackage{subfig}
\usepackage[utf8]{inputenc}
\def\tightlist{}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{pdflscape}
\usepackage{svg}
\usepackage{lineno}
\usepackage{setspace}
\newcommand*{\doverline}[1]{\overline{\overline{#1}}}
\usepackage{tabu}

@@

\title{Towards a robust desicion tool for ecosystems services in the industrial systems: A case study of Distributed recycling for additive manufacturing}
\author{}
\date{\vspace{-2.5em}}

@@

The current ecological urgency confirms that the understanding and managing the interactions between humans systems and the rest of nature is a major prerequisite for addressing the worsening environmental and social crises of the \(21^{st}\) century (\protect\hyperlink{ref-Lomborg2020}{Lomborg 2020}).
Even though engineering products and processes might meet the needs of the present, many of the technological developments are compromising the ability of future generations to meet their own needs (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
For claiming for sustainability in technological development and interventions, the human activities should not exceed critical ecosystem capacity (\protect\hyperlink{ref-Bakshi2018}{Bakshi, Gutowski, and Sekulic 2018}).
This meta-principle is a imperative but not sufficient condition for sustainability.
Moreover, no country currently meets minimum thresholds for social development without exceeding planetary boundaries (\protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
Therefore, it is no possible to rely only on techno-centric interventions without considering the finite planetary ecosystem characterized by profound uncertainty and the shared goals of ecological sustainability and just distribution (\protect\hyperlink{ref-ref}{\textbf{ref?}}).
We need to integrate ecological carrying capacity since the fuzzy front end phase of an industrial systems.
However, the integration of ecological aspects in the decision-making seems not evident given the complexity to define the boundaries and interactions of industrial and ecological systems.

\protect\hyperlink{ref-Ceschin2016}{Ceschin and Gaziulusoy} (\protect\hyperlink{ref-Ceschin2016}{2016}) putted forward the evolution of \emph{Design for Sustainability (DfS)} framework showing the different approaches that have evolved from a product innovation level to socio-technical systems level.
They pointed out that engineering interventions at only technological unit operation/product level are necessary, but not sufficient condition for sustainability.

The economic valuation of ecosystem goods and services gives an elegant framework highlighting their importance for society and human welfare.
However, there is a need to explicitly account for their contribution when designing and developing products and services (\protect\hyperlink{ref-Diwekar2021}{Diwekar et al. 2021}).
The engineering discipline developed the implicit assumption that ecological systems have nearly endless capacity to provide resources and adsorb wastes.
This blindness in the engineering vision can be explaining by the fact that at the beginning of the technological industrialization, the human activites' impacts on the earth remained marginal. This scenario is not true today.
The need for ecosystem services research has become evident due to the impacts of population growth, economic activities, and urbanization on natural capital (\protect\hyperlink{ref-Torres2021}{Torres, Tiwari, and Atkinson 2021}).
The loss in value associated with biodiversity loss and the related loss of ecosystem services is often invisible and does not influence decision makers (\protect\hyperlink{ref-Bruel2018}{Bruel et al. 2019}).
It is difficult to provide information about pressure from industrial systems in corporate information systems.
Engineering within ecological constraints need to acknowledge the capacity of relevant ecosystems to supply the demanded goods and services while the ecosystems and natural capital must be protected, restored and developed to be capable of continuing to supply those services that industry (and society) relies on (\protect\hyperlink{ref-Bakshi2018}{Bakshi, Gutowski, and Sekulic 2018}).

According to the Milleniums 15 out of 24 ecosystems services examined are degraded or being used in an unsustainable manner (\protect\hyperlink{ref-MEA2005}{MEA 2005}).
Likewise, using the planetary boundaries framework, it is argued that anthropogenic activities already exceed the biophysical limits of the ``safe operating zone'' in terms of carbon and nitrogen cycles, and biodiversity loss (\protect\hyperlink{ref-Rockstrom2009}{Rockström et al. 2009}; \protect\hyperlink{ref-ONeill2018}{O'Neill et al. 2018}).
Among the root causes of ecological degradation is ignorance about the exceed of the ecological carrying capacity in many decisions (\protect\hyperlink{ref-Liu2019g}{Liu and Bakshi 2019}; \protect\hyperlink{ref-Rodrigues2021}{Rodrigues et al. 2021}).
Another crucial issue is that current design approaches based on life cycle characterization and footprint methods focus on continuous improvement by reducing life cycle impacts per unit of product, encouraging improvements by doing ``less bad,'' which need not translate into keeping human activities within ecological constraints.
Ideally, it is needed to (re)designed industrial activities to reduce the demand for the demand of ecosystems services creating for a local `\emph{island of sustainability}' (\protect\hyperlink{ref-Wallner1996}{Wallner, Narodoslawsky, and Moser 1996}) which is that the demand should not exceed the supply at the local scale (\protect\hyperlink{ref-Gopalakrishnan2016}{Gopalakrishnan, Bakshi, and Ziv 2016}).
Therefore, it's urgent to expand the boundaries for engineering design from the lowest molecular level to the process level, and from individual process to the higher levels of value chains, ecosystems and the planet (\protect\hyperlink{ref-Martinez-Hernandez2017}{Martinez-Hernandez 2017}).

\protect\hyperlink{ref-Bakshi2015}{Bakshi, Ziv, and Lepech} (\protect\hyperlink{ref-Bakshi2015}{2015}) reported a framework of Techno-Ecological Synergy (TES) in order to expand the scope of the usual techno-centric perspectives.
The main point argued is that TES develops ways of enhancing synergies between a local scale manufacturing process and the land around it.
The final aims is to encourage a more robust analysis of technological and ecological systems at multiple spatial scales ranging from local (e.g.~for small systems such as a house and its yard, a manufacturing process and its site) to a larger scale systems that extend to consider the entire life cycle.

The main purpose of this article is to propose a methodology in order to evaluate the techno-ecological synergy with identifying relative and absolute sustainability aspect of prospective industrial systems.
This methodology is based in the integration of the ecosystem services supply and demand analysis with the purpose to identify scenarios and design improvements.
As a case application, the study of distributed recycling manufacturing will be describe.
Plastic pollution is a global concern that must be addressed collectively with the utmost priority because it endangers the ecosystem and all life forms (\protect\hyperlink{ref-Kumar2021}{Kumar et al. 2021}).
Therefore, new approaches need to be explored in order to reduce ar at least recycling this material.
Thus, this study intends to explore the local impact derived from the implementation of a distributed plastic recycling chain in a territory.

@@

The CICES scheme, on the other hand, refers to ES specifically as the products from ecosystem, which can be directly used by human-beings {[}70{]}.
With this definition, supporting services defined in MEA scheme are excluded from CICES scheme, because supporting services cannot be directly consumed by human beings.
The product-based CICES framework can enable clearer mapping between ecological and economic products.
The hierarchical structure of CICES scheme has provisioning, regulating and cultural services at the highest (section) level.
The following levels organize ES according to their divisions, groups and classes.
At lower levels, more specific services can be defined and characterized.
For example, at section level, we may have only the provisioning service but at class level, we may define the service to be forage grass cultivated as animal feed.
Therefore, the hierarchical structure can supply different levels of detail needed by decision makers.

Figure 2.2 demonstrates the hierarchical structure of CICES scheme.

@@

@@

Three main elements needs to be carry out in this phase: 1) definition of the technological and ecological spheres, 2) prioritization of the territorial issues, and 3) identification of the industrial issues.
